SFJ: An implementation of Semantic Featherweight Java

### 2020-04-23 conference/camera ready/paper.tex
no need for typing

It is worth noticing that the subtyping algorithm finds all nominal and structural subtypes of a given type.
This is due to the fact that all pairs of types are inspected.
Recall from \autoref{sec:intro} that nominal subtyping is name-based and given by the class hierarchy defined by the programmer, whereas structural subtyping is structure-based and given by the set-inclusion of fields and methods.
In particular, it is contra-variant with respect to this set-inclusion.
\autoref{alg:subtyping} finds all structural subtypes of a given class because it checks that its fields and methods are a superset of existing types in $relation$.
On the other hand, it also finds all nominal subtypes because a class inherits all fields and methods of its superclass and as such its fields and methods are a superset of its superclass.
This means that checking for structural subtyping is enough because nominal subtyping will be captured due to inheritance of fields and methods.

@@

\subsection{Type system for SFJ}

The subtyping relation generated by \autoref{alg:subtyping} is used in the type system for SFJ terms, given in \autoref{sec:terms}.
The complete type system and its properties are presented in relevant work \cite{Dardha2013,Dardha2017} and are beyond the scope of this paper.
Let us briefly comment on typing expressions in SFJ.
Field access $e.a$, method call $e.m(e)$, variables $x$ and object creation $\synnew C(\wt{e})$ are typed in the same way as in Java.

For the constants $c$, these are the literal values in our language such as $42$, $3.14$ or $True$.
In most languages such as Java, literal values are cast to the type that is expected in the context they are used.
For example, a method $\textbf{int}\ getNum()\{return\ 42\}$ automatically casts the value to the type $int$.

>>>>

It is worth noticing that the subtyping algorithm finds all nominal and structural subtypes of a given type. This is due to the fact that all pairs of types are inspected.
Recall from \autoref{sec:intro} that nominal subtyping is name-based and given by the class hierarchy defined by the programmer, whether structural subtyping is structure-based and given by the set-inclusion of fields and methods. In particular, it is contra-variant with respect to this set-inclusion.
\autoref{alg:subtyping} finds all structural subtypes of a given class because it checks that its fields and methods are a superset of existing types in $relation$. For example, all classes are structural subtypes of type $empty = []$.
On the other hand, it also finds all nominal subtypes because a class inherits all fields and methods of its superclass and as such its fields and methods are a superset of its superclass.
This means that checking for structural subtyping is enough because nominal subtyping will be captured due to inheritance of fields and methods.

@@

% \subsection{Type system for SFJ}
% The subtyping relation generated by \autoref{alg:subtyping} is used in the type system for SFJ terms, given in \autoref{sec:terms}.
% The complete type system and its soundness properties are presented in relevant work \cite{Dardha2013,Dardha2017} and are beyond the scope of this paper.
% However, let us briefly comment on typing terms in SFJ.
% A program $(\tilde L,e)$ is well typed if both $\tilde{L}$ and $e$ are well typed.
% Class declaration $L$ and method declaration $M$ are well typed if all their components are well typed.
% Let us move onto expressions.
% Field access $e.a$, method call $e.m(e)$ and object creation $\synnew C(\wt{e})$ are typed in the same way as in Java: we inspect the type of the field and the type of the method and its arguments to determine the type of the field access and method call, respectively. The type of an object creation is determined by the type of its class.
% Constants are typed by their basic type.

% Subtyping generated in \autoref{alg:subtyping} is used in a subsumssion typing rule:
% $$
% \frac{\Gamma\vdash e:\alpha_1 \qquad \alpha_1 \leq \alpha_2}{\Gamma \vdash e:\alpha_2}
% $$
% We read this typing rule as follows:
% If an expression $e$ is of type $\alpha_1$ under a typing context $\Gamma$ (details of a typing context are irrelevant here) and type $\alpha$ is a subtype $\leq$ of $\alpha_2$, then expression $e$ can be typed with $\alpha_2$.
